### 2020-02-01 thesis/paper.tex
reordering and some text

\part{Implementation}

\chapter{Implementation Remarks}

\section{Programming Language and Tools}

For the implementation of my tool my language of choice was Java. With Java there are lots of available implementations for different clustering methods available, including the Frameworks ELKI \cite{10.1007/978-3-540-69497-7_41} and WEKA \cite{10.1145/1656274.1656278}, as well as the machine learning library Smile \cite{javasmile}. To improve the performance in some parts of the tool Java 1.8 was chosen as lowest required version, as it allows to use of parallel streams to easily implement parallelism. Additionally, it is easy to create custom visualizations using the low level draw() method of JComponents in Swing. All visualizations were created using a custom draw() method as this leads to much better performance than using small components for the graphs.

\section{Interfaces and implementing Classes}
To ensure that new or missing methods can easily be added to the tool, all methods where a selection can be made from within the tools can be added to by implementing onto the corresponding interface. To add methods one needs to first implement it and if needed it's OptionsPanel and then add it to the corresponding static method found in the view using it.

The following sections describe which interfaces and standard implementations are available, as well as which methods and classes must be edited to add a new method.

@@

\section{Clustering Algorithms}
Clustering Algorithms can be selected and tuned in the clustering workflow window such that the algorithm is used to create base clustering results for the meta view. For this the following interfaces are relevant:

@@

@@

\section{Meta-Clustering}

\chapter{The Tool}\label{cha:Tool}

@@

\section{Reflection of Work}
bla

>>>>

\part{Implemented Tool}
\chapter{Using the Tool}\label{cha:usingtool}
This chapter describes what a user can do with the newly implemented tool.

\chapter{Implementation}
\section{Programming Language and Tools}
For the implementation of my tool my language of choice was Java. With Java there are lots of available implementations for different clustering methods available, including the Frameworks ELKI \cite{10.1007/978-3-540-69497-7_41} and WEKA \cite{10.1145/1656274.1656278}, as well as the machine learning library Smile \cite{javasmile}. To improve the performance in some parts of the tool Java 1.8 was chosen, making it the lowest required Java version to run it.This was done, as it enables the use of parallel streams which make it simple to parallelize functions. Additionally, it is easy to create custom visualizations using the low level draw() method of JComponents in Swing \cite{javaswing}. All graphs and plots were created using a custom draw() method as this leads to much better performance than using small components for the graphs.

\section{Class Interfaces and Implementations}
To ensure that new or missing methods can easily be added to the tool, all methods where a selection can be made from within the tool can be added to by implementing onto the corresponding interface. To add methods one needs to first implement it and if needed it's OptionsPanel and then add it to the corresponding static method found in the view using it.

The following sections describe which interfaces and standard methods are implemented, as well as which functions and classes must be edited to add a new custom methods.

@@

\subsection{Clustering Algorithms}
Clustering Algorithms can be selected and tuned in the clustering workflow window such that the algorithm is used to create base clustering results for the meta view. For additional information on the algorithms themselves, see Section [REFERENCE] The following interfaces are relevant for clustering:

@@

bla bla bla

@@

bla bla bla

\subsection{Meta-Clustering}

bla bla bla

\subsection{Consensus Clustering}

bla bla bla

\section{Visualization}

To visualize the data in different ways and provide a functional Graphical User Interface (GUI) the Java Swing \cite{javaswing} Toolkit was used. It allows for both high level calls creating objects withing windows, e.g. panels, buttons or combo-boxes, as well as low level calls by directly changing the behavior of the draw() function. For the basic GUI the panels and buttons of the tool were created with high level calls, while the different graphs and plots were implemented by overriding the draw() function. Overriding the draw() function immensely improved performance as the already available high level objects are computationally costly, when needing many of them, by comparison.

\subsection{Scatter Plot}

bla bla bla

\subsection{Switching between Clusterings}

bla bla bla

\subsection{Scatter Plot Matrix}

bla bla bla

\subsection{OPTICS Plot}

bla bla bla

\subsection{Heat Map}

bla bla bla

\subsection{Filter Panel}

bla bla bla

\subsection{Cluster comparison}

bla bla bla

@@

\section{Reflection of Work}
In this article I showed
